Automated inference of production rules for glycans

### 2021-04-19 papers/sugar-synth/variations.tex
changes to appendix

We have presented a simplified version of
the biological problem.
% However, the biological problem has more details.
We have developed variations of the above method to support more realistic problems.

>>>>

We have presented a simplified version of
the biological problem. However, in real settings, we often encounter many more variants which require us to support additional constraints to model the set of molecules and possible rules in that particular problem. Hence, we developed the following variations of the method described in the main text to support more realistic problems.
% However, the biological problem has more details.
% We have developed variations of the above method to support more realistic problems.
